The influence of massive early merger events on the chemo-dynamics of galaxy discs

### 2022-10-13 src/tex/ms.tex
[showyourwork] overleaf sync

%%%%%%%%%%%%%%%%%% FIGURE 1 %%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\begin{center}

\end{center}
\vspace{-.35cm}
\caption{}
\label{fig:param1}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% TABLE 2 %%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
\label{tab:props}
\begin{center}
\caption{Yield tables implemented in Chempy.}
\begin{minipage}{.5\textwidth}
\begin{tabular}{l c c }
		\hline\hline
		Yield Table & Masses & Metallicities \\
		%  &  & [$\Msun$] &  \\
		\hline
		\multicolumn{3}{c}{CC SN}\\
		\hline
		\citet{Portinari1998} & [6,120] & [0.0004,0.05] \\
		\citet{Francois2004} & [11,40] & [0.02] \\
		\citet{Chieffi2004} & [13,35] & [0,0.02] \\
		\citet{Nomoto2013} & [13,40] & [0.001,0.05] \\
		\citet{Frischknecht2016} & [15,40] & [0.00001,0.0134] \\
		West \& Heger (in prep.) & [13,30] & [0,0.3] \\
		\citet{Ritter2018} & [12,25] & [0.0001,0.02] \\
		\citet{Limongi2018}\footnote{Using the rotation parametrization of \citet{Prantzos2018}} & [13,120] & [0.0000134,0.0134] \\
		\hline
		\multicolumn{3}{c}{SN$_{\rm Ia}$}\\
		\hline
		\citet{Iwamoto1999} & [1.38] & [0,0.02] \\
		\citet{Thielemann2003} & [1.374] & [0.02] \\
		\citet{Seitenzahl2013} & [1.40] & [0.02] \\
		\hline
		\multicolumn{3}{c}{AGB}\\
		\hline
		\citet{Karakas2010} & [1,6.5] & [0.0001,0.02] \\
		\citet{Ventura2013} & [1,6.5] & [0.0001,0.02] \\
		\citet{Pignatari2016} & [1.65,5] & [0.01,0.02] \\
		\citet{Karakas2016} & [1,8] & [0.001,0.03] \\
		TNG\footnote{The TNG yield set for AGB stars is a mixture of yields taken from \citet{Karakas2010,Doherty2014} and \citet{Fishlock2014}} & [1,7.5] & [0.0001,0.02] \\
		\hline
		\multicolumn{3}{c}{Hypernova}\\
		\hline
		\citet{Nomoto2013} & [20,40] & [0.001,0.05] \\
        \hline
\end{tabular}
\end{minipage}
\end{center}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%% FIGURE 1 %%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
    \script{half_mass_radius_gas.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/2.79e12_gas_size.pdf}
        \caption{
            Half mass radius of the cold gas as a function of time. Sudden increase around 2, 3 and 9 Gyr clearly signify the gas rich merger events this galaxy undergoes.
        }
        \label{fig:half_mass}
    \end{centering}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
